Clustering in a hyperbolic model of complex networks.

### 2020-03-10 introduction.tex
Edits by Tobias

\begin{figure}[!t]
\centering
\includegraphics[scale=0.3]{figures/KPKVB.png}
\caption{Simulation $G(n;\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.
%\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
}
\label{fig:H_graph_example}
\end{figure}

@@

As observed by Krioukov et al.~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
% More specifically, if $N_k$ denotes the number of vertices of degree exactly $k$ then Gugelmann et al.~\cite{gugelmann2012random} have shown that
% 
% \begin{equation}\label{eq:gugeldegseq} 
% N_k = (1+o(1)) \cdot n \cdot p_k \quad \text{ a.a.s., }
% \end{equation}
% 
% \noindent
% where $p_k := 2\alpha \cdot \xi^{2\alpha} \cdot \Gamma^+\left(k - 2\alpha, \xi\right) / k!$
% with, here and in the rest of the paper, $\xi := \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and 
% $\Gamma^+(a,b) := \int_b^\infty t^{a-1} e^{-t} \text{d}t$ the 
% {\em upper incomplete gamma function} and, for $(E_n)_n$ a sequence of events, 
% $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
%%In particular $X_n = (1+o(1)) Y_n$ is equivalent to $X_n/Y_n \plim 1$.
%In fact~\eqref{eq:gugeldegseq} was shown in~\cite{gugelmann2012random} to hold not only when $k$ is constant but 
%also if $k$ depends on $n$ as long as $k = o( n^\delta )$ for a suitable small constant $\delta = \delta( \alpha )$.
%Standard asymptotic manipulations show that 
%
%$$p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha+1)}, $$
%
%as $k\to\infty$.
%\TM{ \RD{We need to add something like the following} : 
%In Appendix~\ref{} we settle the minor technical point of showing that~\eqref{eq:gugeldegseq} in fact extends 
%to all $k$ with $k \ll n^{1/(2\alpha+1)}$, while 
%$N_k = 0$ a.a.s.~whenever $k \gg n^{1/(2\alpha+1)}$. }
Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s. Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Prob{E_n} \to 1$ as $n \to \infty$. Here the events $E_n$ might be defined in different probability spaces, in which case $\Pee$ will the corresponding probability measure.
%Their work however left open the question of whether the clustering coefficient actually converges in probability.

@@

For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in probability to $X$, as $n \to \infty$.

@@

Our first result is the following.

@@

In the above expression for $\gamma$, a factor $\alpha-1$ occurs in the denominator of each term, but we will see that this
corresponds to a removable singularity. We have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

Our second result is on the clustering function for constant $k$.

@@

\[
	c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k),
\]
where $\gamma(k)$ is defined for $\alpha \ne 1$ as 
\begin{align*}
\gamma(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
\end{align*}
and for $\alpha = 1$ as the $\alpha\to1$ limit of the above expression.
% \begin{align*}
% 	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
% 		\Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
% 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
% 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
% \end{align*}
% with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
\end{theorem}

\noindent
A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25Squares.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity. Again, we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

\begin{theorem}\label{thm:mainktoinfty}
Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence of non-negative integers
satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have
\[
	\E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{\gamma(k_n)},
\]
as $n \to \infty$, where $\gamma(\cdot)$ is as in Theorem~\ref{thm:mainkfixed}. In particular
\[
	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{\gamma(k_n)}- 1 \right|} = 0.
\]
\end{theorem}

@@

To clarify the scaling behaviour of $\gamma(k)$ with $k$ we offer the following result.

@@

$$ \gamma(k) = 
(1+o(1)) \cdot \left\{ \begin{array}{cl}
\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
\frac{6 \nu}{\pi} \cdot \frac{\log(k)}{k}& \text{ if } \alpha = \frac{3}{4},\\
 c_{\alpha} \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 
\end{array} \right.,
$$
where $c_{\alpha} := \left( \frac{3\alpha - 1}{2^{4\alpha+1}\alpha(\alpha-1)^2} 
	+ \frac{(\alpha - \frac{1}{2})B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)}{2(\alpha - 1)\alpha} 
	- \frac{B(2\alpha, 3\alpha - 4)}{4(\alpha - 1)} \right)  \cdot \xi^{4\alpha-2}$.
\end{proposition}

Note that Theorem~\ref{thm:mainktoinfty} implies that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows, whose scaling is given in the above result. In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.

@@

\subsection{Observations}

There are a few other observation to be made regarding our results.

\paragraph{Uniform convergence.}

Our results for the local clustering function in particular imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. To see this let
\[
	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
\]
Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainktoinfty}
\[
	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
\]

\paragraph{Near maximum scaling for $k_n$.}
Our results for the clustering function in the KPKVB model are valid for any sequence of non-negative integers $k_n \to \infty$ such that $k_n \ll n^{\frac{1}{2\alpha + 1}}$. Although one would like to have results for any sequence $k_n \le n-1$, it turns out that $n^{1/(2\alpha + 1)}$ is the near maximum scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true. To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_clustering_function} we have that $c(k_n; G_n) = 0$ if $N_{n}(k_n) = 0$, where $N_n(k_n)$ denotes the number of vertices in a KPKVB graph $G(n; \alpha, \nu)$ with degree $k_n$. It follows by Markov's inequality that for any positive function $f : \R_+ \to \R_+$
\begin{align*}
	\Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
	&\ge \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|\ind{N_n(k_n) = 0}}\\ 
	&\ge \Prob{N_{n}(k_n) = 0} \ge 1 - \Exp{N_n(k_n)}.
\end{align*}
We shall later establish (see Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}) that $\Exp{N_n(k_n)}$ scales as $n k_n^{-(2\alpha + 1)}$. Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that 
\[
	\lim_{n \to \infty} \Exp{N_{n}(k_n)} = 0
\]
and hence
\[
	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
	\ge 1 - \lim_{n \to \infty} \Exp{N_{n}(k_n)} = 1 \ne 0,
\]
for any positive function $f$. This implies that we cannot expect a result like that of Theorem~\ref{thm:mainktoinfty} to hold as soon as $k_n \gg n^{\frac{1}{2\alpha + 1}}$.

\paragraph{Transition in scaling at $\bm{\alpha = 3/4}$.}

It follows from Proposition~\ref{prop:asymp} that there is a transition in the scaling of the local clustering function at $\alpha = 3/4$. This corresponds to an exponent $5/2$ for the probability mass function of the degree distribution. This transition is different from those often observed for networks with scale-free degree distributions, where transitions occur at integer values of the exponent. At this point, it is unclear what the underlying reason is for the appearance of the transition at this half exponent. Interestingly, a similar transition point has also been observed for both majority vote models~\cite{chen2015critical} and flocking dynamics~\cite{miguel2018effects} on networks with scale-free degree degree distributions.

@@

The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be a lot more involved. The main reason for this is that we push the possible scaling of $k_n$ to its maximum and hence a great deal of work is needed to properly control the arising error terms and make sure these are of smaller order than $\gamma(k_n)$.

Finally, the Appendix includes some technical results on Meijer's G-function, Chernoff bounds for Poisson and Binomial random variables and the code used for simulations.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[scale=0.3]{figures/KPKVB.png}
\caption{Simulation $G(n;\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.}
\label{fig:H_graph_example}
\end{figure}

@@

As observed by Krioukov et al.~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the 
degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the 
constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing 
in the sense that it is bounded below by a positive constant a.a.s. 
Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means 
that $\Prob{E_n} \to 1$ as $n \to \infty$.

@@

For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in 
probability to $X$, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense 
(i.e.~if $\Ee |X_n-X| \to 0$.)

@@

Our first main result shows the convergence of the local clustering coefficient in the KPKVB model and 
establishes the limit exactly.

@@

In the above expression for $\gamma$, a factor $\alpha-1$ occurs in the denominator of each term, but we will see that this
corresponds to a removable singularity. We have not been able to find a closed form expression in terms of standard functions in the case 
when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

Our second main result is on the clustering function for constant $k$.

@@

\[
	c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k),
\]
where $\gamma(k)$ is defined for $\alpha \ne 1$ as 
\begin{align*}
\gamma(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
\end{align*}
and for $\alpha = 1$ as the $\alpha\to1$ limit of the above expression.
\end{theorem}

\noindent
A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25Squares.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity. 
Again, we have not been able to find a closed form expression in terms of standard functions in the case when $\alpha=1$, but in 
Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

\begin{theorem}\label{thm:mainktoinfty}
Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence of non-negative integers
satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have

$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L_1} 1. $$

\end{theorem}

\noindent
The conclusion of Theorem~\ref{thm:mainktoinfty} is slightly stronger than $c(k_n; G_n)/\gamma(k_n) 
\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community.

@@

To clarify the scaling behaviour of $\gamma(k)$ we offer the following result.

@@

$$ \gamma(k) = 
\left\{ \begin{array}{ll}
(c_{\alpha,\nu}+o(1)) \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
(c_{\alpha,\nu}+o(1)) \cdot \frac{\log(k)}{k}& \text{ if } \alpha = \frac{3}{4},\\
(c_{\alpha,\nu}+o(1)) \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 
\end{array} \right.,
$$
where

$$ c_{\alpha,\nu} := 
\left\{ \begin{array}{cl}
8\alpha \nu / (\pi\left(4\alpha - 3\right)) & \text{ if } \alpha > \frac{3}{4}, \\
6 \nu / \pi & \text{ if } \alpha = \frac{3}{4},\\
 \left( \frac{3\alpha - 1}{2^{4\alpha+1}\alpha(\alpha-1)^2} 
	+ \frac{(\alpha - \frac{1}{2})B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)}{2(\alpha - 1)\alpha} 
	- \frac{B(2\alpha, 3\alpha - 4)}{4(\alpha - 1)} \right)  \cdot \xi^{4\alpha-2} 
	& \text{ if } \frac12 < \alpha < \frac34.
\end{array} \right. $$
\end{proposition}

Theorem~\ref{thm:mainktoinfty} states that the clustering function of the KPKVB model scales as $\gamma(k)$ as the number of vertices $n\to\infty$, and
Proposition~\ref{prop:asymp} makes clear how $\gamma(k)$ behaves as $k$ grows.
In particular, these results contradict the scaling conjectured in~\cite{krioukov2010hyperbolic} for 
$\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.

@@

\subsection{Additional observations and results}

There are a few additional remarks we would like to make regarding our results.

\subsubsection{The degree distribution and the range of $k_n$ in Theorem~\ref{thm:mainktoinfty}}

The reader may already have observed that, with a power law exponent of $2\alpha+1$ for the probability mass function of 
the degree sequence, we would expect $\Theta( n \cdot k^{-(1+2\alpha)} ) = o(1)$ vertices of degree {\em exactly} $k$ whenever
$k \gg n^{1/(1+2\alpha)}$.

This is the reason why in Theorem~\ref{thm:mainktoinfty} we restrict ourselves to 
sequences $k_n$ with $k_n \ll n^{1/(1+2\alpha)}$. 
When  $k_n \gg n^{1/(1+2\alpha)}$ there are no vertices of degree exactly $k_n$ a.a.s., which in particular
implies that the clustering function equals zero a.a.s.~for any such sequence $k_n$.
%When $k_n$ is of the same order as $n^{1/(1+2\alpha)}$ then the probability that there are no vertices of degree exactly $k_n$
%stays bounded away from zero.

As mentioned previously, Gugelmann et al.~\cite{gugelmann2012random} gave a mathematically rigorous result on the degree sequence, which can of course be rephrased as a result on the number of nodes with degree exactly $k$. 
Their results allow $k = k_n$ to grow with $n$, but unfortunately require that $k_n \leq n^\delta$ with 
$\delta < \min\left\{\frac{2\alpha-1}{4\alpha(2\alpha +1)}, \frac{2(2\alpha -1)}{5(2\alpha + 1)}\right\} < \frac{1}{2\alpha + 1}$.
For completeness we offer the following result, which extends that of Gugelmann et al.~to the full range $1 \le k_n \le n-1$.

\begin{theorem}\label{thm:degrees_hyperbolic}
Let $\alpha >\frac{1}{2}, \nu > 0$, denote by $N_n(k)$ the number of vertices with degree $k$ in the KPKVB model $G(n;\alpha,\nu)$ and 
consider a sequence of integers $(k_n)_n$ with $0 \leq k_n \leq n-1$.
\begin{enumerate}
\item If $k_n \ll n^{\frac{1}{2\alpha+1}} $ as $n\rightarrow \infty$, then a.a.s.

$$N_n(k_n) = (1+o(1)) \cdot n \cdot \pmf(k_n),$$

where $\pmf(k_n) = 2\alpha \xi^{2\alpha}\Gamma^+(k_n-2\alpha,\xi)/k_n!$.

\item If $k_n = (1+o(1))c n^{\frac{1}{2\alpha+1}}$ for some fixed $c >0$, then

$$ N_n(k_n) \xrightarrow[n\rightarrow\infty]{d} \operatorname{Po}(2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}). $$

\item If $k_n \gg n^{\frac{1}{2\alpha+1}}$, then a.a.s. $N_n(k_n) = 0$.
\end{enumerate}
\end{theorem}

\subsubsection{Transition in scaling at $\alpha = 3/4$.}

Proposition~\ref{prop:asymp} demonstrates that there is a transition in the scaling of the local clustering 
function at $\alpha = 3/4$. 
This corresponds to an exponent $5/2$ for the probability mass function of the degree distribution. 
This transition is different from those often observed for networks with scale-free degree distributions, where transitions occur at
integer values of the exponent. 
At this point, it is unclear what the underlying reason is for the appearance of the transition at this particular half integer 
exponent. 
Interestingly, a similar transition point has also been observed for both majority vote models~\cite{chen2015critical} and 
flocking dynamics~\cite{miguel2018effects} on networks with scale-free degree degree distributions.

\subsubsection{Uniform convergence.}

Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
Now let
\[
	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
\]
Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
\[
	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
\]

@@

In Section~\ref{sec:degrees} we prove Theorem~\ref{thm:degrees_hyperbolic}, which also doubles as a warm-up for the proof 
of Theorem~\ref{thm:mainktoinfty} of the clustering function for growing $k$.
The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be technically involved.
The main reason for this is that when we push $k_n$ close to the maximum possible value, a great deal of work is needed 
to properly control the arising error terms.

The Appendix includes some auxiliary results on Meijer's G-function, Chernoff bounds for Poisson and Binomial 
random variables and the code used for simulations.
